Batch Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-02-08 paper/experiments.tex
Paper update

The mean convergence plot is given in Figure~\ref{fig:resClassE}. We can see
that the MACE outperformed the BLCB and EI-LP in both sequential and batch
mode. For the batch runs, the MACE convergences fastest among the three
algorithms, while the sequential MACE has similar performance as the batch
EI-LP method.

>>>>

The mean convergence plot is given in Figure~\ref{fig:resClassE}, the mean and
standard deviation of the final FOM values are listed in
Table~\ref{tab:result_PA}. We can see that the MACE outperformed the BLCB and
EI-LP in both sequential and batch mode.  For the batch runs, the MACE
convergences fastest among the three algorithms, while the sequential MACE
algorithm while the sequential MACE has similar performance as the batch EI-LP
method.
